---
title: "Preliminary Results"
author: Tobias Schnabel
date: June 18, 2023
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


DGP 1: One treatment group, TE is unit-and time- homogeneous

```{r}
print(analyze_sim_results(load_sim_results()))
```

DGP 2: One treatment group, TE is unit-homogeneous, time-varying

```{r}
print(analyze_sim_results(load_sim_results()))
```

DGP 3: Multiple Treatment Groups, Time-Invariant Homogeneous TE 

```{r}
print(analyze_sim_results(load_sim_results()))
```

DGP 4: Multiple Treatment Groups,Time-Invariant Heterogeneous TE

```{r}
print(analyze_sim_results(load_sim_results()))
```

DGP 5: Multiple Treatment Groups, Time-Varying Homogeneous TE 

```{r}
print(analyze_sim_results(load_sim_results()))
```

DGP 6: Multiple Treatment Groups, Time-Varying Heterogeneous TE 

```{r}
print(analyze_sim_results(load_sim_results()))
```

DGP 7: Multiple Treatment Groups, Time-Varying Heterogeneous TE, **Parallel Trends Violated**

```{r}
print(analyze_sim_results(load_sim_results()))
```

