---
title: "Simulation Results"
author: Tobias Schnabel
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    self_contained: no
    theme: flatly
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("packages.R")
source("Functions.R")
library(DT)
load_all_results()
plot_html(1, F)
```
<style type="text/css">
table th {
    text-align: left !important;
}
</style>


# DGP 1: One treatment group, TE is unit-and time- homogeneous

```{r, echo=FALSE}
dgp_plot(dgp_1_sim(), "", 1)
results_html(sim1, "static")
plot_est_dens(sim1, F)
```


# DGP 2: One treatment group, TE is unit-homogeneous, time-varying

```{r, echo=FALSE}
dgp_plot(dgp_2_sim(), "", 2)
results_html(sim2, "dynamic")
plot_est_dens(sim2, T)
```

# DGP 3: Multiple Treatment Groups, Time-Invariant Homogeneous TE 

```{r, echo=FALSE}
dgp_plot(dgp_3_sim(), "", 3)
results_html(sim3, "static")
plot_est_dens(sim3, F)
```

# DGP 4: Multiple Treatment Groups,Time-Invariant Heterogeneous TE

```{r, echo=FALSE}
dgp_plot(dgp_4_sim(), "", 4)
results_html(sim4, "static")
plot_est_dens(sim4, F)
```

# DGP 5: Multiple Treatment Groups, Time-Varying Homogeneous TE 

```{r, echo=FALSE}
dgp_plot(dgp_5_sim(), "", 5)
results_html(sim5, "dynamic")
plot_est_dens(sim5, T)
```

# DGP 6: Multiple Treatment Groups, Time-Varying Heterogeneous TE 

```{r, echo=FALSE}
dgp_plot(dgp_6_sim(), "", 6)
results_html(sim6, "dynamic")
plot_est_dens(sim6, T)
```

# DGP 7: Multiple Treatment Groups, Time-Varying Heterogeneous TE, **Unconditional** Parallel Trends Violated

```{r, echo=FALSE}
dgp_plot(dgp_7_sim(), "", 7)
results_html(sim7, "dynamic")
plot_est_dens(sim7, T)
```

# DGP 8: Multiple Treatment Groups, Time-Varying Heterogeneous TE, **Parallel Trends Violated**

```{r, echo=FALSE}
dgp_plot(dgp_8_sim(), "", 8)
results_html(sim8, "dynamic")
plot_est_dens(sim8, T)
```
