---
title: "Simulation Results"
author: Tobias Schnabel
date: "Last compiled on `r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    self_contained: no
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
source("packages.R")
source("Functions.R")
library(DT)
load_all_results()
```

```{=html}
<style type="text/css">
table th {
    text-align: left !important;
}
</style>
```
## Instructions to replicate can be found [here](https://github.com/tobias-schnabel/matrix-completion/blob/main/Replication.md)

# Full thesis can be found [here](https://github.com/tobias-schnabel/matrix-completion/blob/main/Thesis_Schnabel.pdf)

# Simulation 1: One treatment group, TE is unit-and time- homogeneous

```{r Sim1}
dgp_plot(dgp_1_sim())
results_html(sim1)
plot_est_dev(sim1)
plot_est_dens(sim1)
```

# Simulation 2: One treatment group, TE is unit-homogeneous, time-varying

```{r Sim2}
dgp_plot(dgp_2_sim())
results_html(sim2)
plot_est_dev(sim2)
plot_est_dens(sim2)
```

# Simulation 3: Multiple Treatment Groups, Time-Invariant Homogeneous TE

```{r Sim3}
dgp_plot(dgp_3_sim())
results_html(sim3)
plot_est_dev(sim3)
plot_est_dens(sim3)
```

# Simulation 4: Multiple Treatment Groups,Time-Invariant Heterogeneous TE

```{r Sim4}
dgp_plot(dgp_4_sim())
results_html(sim4)
plot_est_dev(sim4)
plot_est_dens(sim4)
```

# Simulation 5: Multiple Treatment Groups, Time-Varying Homogeneous TE

```{r Sim5}
dgp_plot(dgp_5_sim())
results_html(sim5)
plot_est_dev(sim5)
plot_est_dens(sim5)
```

# Simulation 6: Multiple Treatment Groups, Time-Varying Heterogeneous TE

```{r Sim6}
dgp_plot(dgp_6_sim())
results_html(sim6)
plot_est_dev(sim6)
plot_est_dens(sim6)
```

# Simulation 7: Multiple Treatment Groups, Time-Varying Heterogeneous TE, **Unconditional** Parallel Trends Violated

```{r Sim7}
dgp_plot(dgp_7_sim())
results_html(sim7)
plot_est_dev(sim7)
plot_est_dens(sim7)
```

# Simulation 8: Multiple Treatment Groups, Time-Varying Heterogeneous TE, **Parallel Trends Violated**

```{r Sim8}
dgp_plot(dgp_8_sim())
results_html(sim8)
plot_est_dev(sim8)
plot_est_dens(sim8)
```
